---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE
)
```


# PeakABro
Peaklist Annotator and Browser

The purpose of this package is to help identification in metabolomics by:
1) extracting tables of compounds with their relevant info from different compound database formats
2) annotating an XCMS (or other) peaklist with the compounds from the compound databases
3) displaying an interactive browseable peaktable with the annotated compounds in nested tables

## Get compound tables from databases

Several compound databases can be downloaded and from and their database format we can extract a table of relevant information.
So far I have added functions to extract in from the downloadable LipidMaps and LipidBlast.

* Download the LipidMaps SDF from: http://www.lipidmaps.org/resources/downloads/
* Download the LipidBlast json from: http://mona.fiehnlab.ucdavis.edu/downloads
* Adjust path to where you have downloaded the files.

```{r, cache=TRUE}
library(PeakABro)
lipidmaps_tbl <- generate_lipidmaps_tbl("inst/extdata/LMSDFDownload6Dec16FinalAll.sdf")
lipidblast_tbl <- generate_lipidblast_tbl("inst/extdata//MoNA-export-LipidBlast.json")
```

```{r, cache=TRUE}
lipidmaps_tbl
```

```{r, cache=TRUE}
lipidblast_tbl
```

This takes rather long because the databases are quite large. Therefore I have configured

# Alternatively get pre-made table from the package
```{r, cache=TRUE}
lipidmaps_tbl2 <-  readRDS(system.file("extdata", "lipidmaps_tbl.rds",  package="PeakABro"))
lipidblast_tbl2 <- readRDS(system.file("extdata", "lipidblast_tbl.rds", package="PeakABro"))
```
